### 2021-04-20 paper/ase21/analyzer.tex
[ASE21] Minor typo in analyzer

      &&&&\mid&
      \tnum \mid \tbigint \mid \tstr \mid \tsymb \\
    \end{array}
  $}
  \vspace*{-0.5em}
\end{figure} \noindent
A modified $\ires$ program $\prog = (\getfunc, \getinst, \getnext)$ consists
of three mappings;  $\getfunc: \labset \rightarrow \funcset$
maps labels to their functions, $\getinst: \labset \rightarrow
\instset$ maps labels to their instructions, and $\getnext: \labset
\rightarrow \labset$ maps labels totheir next labels, where a label $\lab \in \labset$
denotes a program point. A function $\kwdef \; \f (\x^*, \kwsl \y^* \kwsr). \;
\lab \in \funcset$ consists of its name $\f$, normal parameters $\x^*$, optional
parameters $\y^*$, and a body label $\lab$.  For presentation brevity,
we assume that no global variables exist in this paper.
An instruction $\inst$ is a variable declaration, a function call, an assertion,
a branch, a return, or a reference update.  An invocation of an abstract
algorithm in ECMAScript is compiled to a function call instruction with a new
temporary variable.  We represent loops using branch instructions with
cyclic pointing of labels in $\getnext$.  A reference $\refer$
is a variable $\x$ or a field access $\refer \kwsl \expr \kwsr$.  We write
$\refer.\f$ to briefly represent $\refer \kwsl \code{"f"} \kwsr$. An
expression $\expr$ is a record, a list, a type check, an existence check, a
binary operation, a unary operation, a reference, a constant, or a primitive,
which is either $\undefval$, $\nullval$, a \jscode{Boolean} $\bool$, a
\jscode{Number} $\num$, a \jscode{BigInt} $\bigint$, a \jscode{String} $\str$,
or a \jscode{Symbol} $\symb$.

@@

\begin{figure*}[t]
  \centering
  \resizebox{0.49\textwidth}{!}{$
    \begin{array}{@{}l@{~}c@{~}l}
      \asemi{\kwlet \; \x = \expr}
      (\lab, \tys)(\aelem) &=&
      (\{ (\getnext(\lab), \tys) \mapsto \aenv[\x \mapsto
      \aseme{\expr}(\aenv)] \}, \emp)\\

@@

            \retp' = \{ (\func, \tys') \mapsto \{ (\getnext(\lab), \tys, \x)
            \} \mid \func \in \aty \;\wedge\; \tys' \in T' \}\\
          \end{array}
        \right.
      }\\
    \end{array}
  $}
  \resizebox{0.49\textwidth}{!}{$
    \begin{array}{@{}l@{~}c@{~}l}
      \asemi{\kwreturn \; \expr}
      (\lab, \tys)(\aelem) &=&
      (\{ (\lab_r, \tys_r) \mapsto \aenv_r \mid
      (\lab_r, \tys_r, \x) \in R\}, \emp)\\
      \multicolumn{3}{@{}l}{
        \text{where} \; R = \retp(\getfunc(\lab), \tys) \;\wedge\; \aenv_r =
        \rmap(\lab_r, \tys_r)[\x \mapsto \aseme{\expr}(\aenv)]
      }\\

@@

      \multicolumn{3}{@{}l}{\text{where} \; \aelem = (\rmap, \retp) \;\wedge\;
      \aenv = \rmap(\lab, \tys)}
    \end{array}
  $}
\caption{Abstract semantics of instructions for a program $\prog = (\getfunc, \getinst, \getnext)$,
$\asemi{\inst}: (\labset \times \tyset^*) \rightarrow \adom \rightarrow \adom$
}
  \vspace*{-1em}
  \label{fig:abs-sem}
\end{figure*}

%    \caption{Instructions with $\asemi{\inst}: (\labset \times \tyset^*)
%    \rightarrow \adom \rightarrow \adom$.}
%  \caption{Abstract semantics of the modified $\ires$ for a program $\prog =
%  (\getfunc, \getinst, \getnext)$}

A type $\ty \in \tyset$ is either a nominal type $\tname$, an empty list type
$\clist{}$, a parametric list type $\clist{\ty}$,
a JavaScript type $\tjs$,
a primitive type $\tprim$,
$\tnumeric$ that is either \jscode{Number} or \jscode{BigInt},
$\tnum$, $\tbigint$, $\tstr$, or $\tsymb$.
A nominal type $\tname$ is either 1) an
\textit{AST type} with its corresponding syntax-directed algorithms as its fields,
or 2) a \textit{record type} with specific fields as described in ECMAScript.
For example, Figure~\ref{fig:record-fields-table} shows an excerpt from
ECMAScript 2020 (ES11) that describes the fields of completion records%
\footnote{https://262.ecma-international.org/11.0/\#table-8}, which we
model as follows:

@@

      \refine(\x : \ty, \true)(\aenv) &=&
      \aenv[ \x \mapsto \aty_\x \meet \{ \ty \} ]\\
      \refine(\x : \ty, \false)(\aenv) &=&
      \aenv[ \x \mapsto \aty_\x \setminus \{ \ty' \mid \ty' \subtype \ty
      \}]\\
      \refine(\expr, \bool)(\aenv) &=& \aenv\\
    \end{array}
  $}
  \vspace*{-0.5em}
\end{figure} \noindent
where $\aenv_j = \refine(\expr_j, \bool)(\aenv)$ for $j = 0, 1$,
$\aty_\expr = \aseme{\expr}(\aenv)$, and $\getSingle{\aty}$
returns $\{ \ty \}$ if $\aty$ denotes a single type $\ty$, or
returns $\emp$, otherwise.

>>>>

      &&&&\mid&
      \tnum \mid \tbigint \mid \tstr \mid \tsymb \\
    \end{array}
  $}
  \vspace*{-0.5em}
\end{figure} \noindent
A modified $\ires$ program $\prog = (\getfunc, \getinst, \getnext)$ consists
of three mappings;  $\getfunc: \labset \rightarrow \funcset$
maps labels to their functions, $\getinst: \labset \rightarrow
\instset$ maps labels to their instructions, and $\getnext: \labset
\rightarrow \labset$ maps labels to their next labels, where a label $\lab \in \labset$
denotes a program point. A function $\kwdef \; \f (\x^*, \kwsl \y^* \kwsr). \;
\lab \in \funcset$ consists of its name $\f$, normal parameters $\x^*$, optional
parameters $\y^*$, and a body label $\lab$.  For presentation brevity,
we assume that no global variables exist in this paper.
An instruction $\inst$ is a variable declaration, a function call, an assertion,
a branch, a return, or a reference update.  An invocation of an abstract
algorithm in ECMAScript is compiled to a function call instruction with a new
temporary variable.  We represent loops using branch instructions with
cyclic pointing of labels in $\getnext$.  A reference $\refer$
is a variable $\x$ or a field access $\refer \kwsl \expr \kwsr$.  We write
$\refer.\f$ to briefly represent $\refer \kwsl \code{"f"} \kwsr$. An
expression $\expr$ is a record, a list, a type check, an existence check, a
binary operation, a unary operation, a reference, a constant, or a primitive,
which is either $\undefval$, $\nullval$, a \jscode{Boolean} $\bool$, a
\jscode{Number} $\num$, a \jscode{BigInt} $\bigint$, a \jscode{String} $\str$,
or a \jscode{Symbol} $\symb$.

@@

\begin{figure*}[t]
  \centering
  \resizebox{0.49\textwidth}{!}{$
\renewcommand{\arraystretch}{1.3}
    \begin{array}{@{}l@{~}c@{~}l}
      \asemi{\kwlet \; \x = \expr}
      (\lab, \tys)(\aelem) &=&
      (\{ (\getnext(\lab), \tys) \mapsto \aenv[\x \mapsto
      \aseme{\expr}(\aenv)] \}, \emp)\\

@@

            \retp' = \{ (\func, \tys') \mapsto \{ (\getnext(\lab), \tys, \x)
            \} \mid \func \in \aty \;\wedge\; \tys' \in T' \}\\
          \end{array}
        \right.
      }\\
    \end{array}
  $}
  \resizebox{0.49\textwidth}{!}{$
\renewcommand{\arraystretch}{1.3}
    \begin{array}{@{}l@{~}c@{~}l}
      \asemi{\kwreturn \; \expr}
      (\lab, \tys)(\aelem) &=&
      (\{ (\lab_r, \tys_r) \mapsto \aenv_r \mid
      (\lab_r, \tys_r, \x) \in R\}, \emp)\\
      \multicolumn{3}{@{}l}{
        \text{where} \; R = \retp(\getfunc(\lab), \tys) \;\wedge\; \aenv_r =
        \rmap(\lab_r, \tys_r)[\x \mapsto \aseme{\expr}(\aenv)]
      }\\

@@

      \multicolumn{3}{@{}l}{\text{where} \; \aelem = (\rmap, \retp) \;\wedge\;
      \aenv = \rmap(\lab, \tys)}
    \end{array}
  $}
\caption{Abstract semantics of instructions for a program $\prog = (\getfunc, \getinst, \getnext)$,
$\asemi{\inst}: (\labset \times \tyset^*) \rightarrow \adom \rightarrow \adom$
}
  \vspace*{-.5em}
  \label{fig:abs-sem}
\end{figure*}

A type $\ty \in \tyset$ is either a nominal type $\tname$, an empty list type
$\clist{}$, a parametric list type $\clist{\ty}$,
a JavaScript type $\tjs$,
a primitive type $\tprim$,
a numeric type $\tnumeric$,
$\tnum$, $\tbigint$, $\tstr$, or $\tsymb$.
A nominal type $\tname$ is either 1) an
\textit{AST type} with its corresponding syntax-directed algorithms as its fields,
or 2) a \textit{record type} with specific fields as described in ECMAScript.
For example, Figure~\ref{fig:record-fields-table} shows an excerpt from
ECMAScript 2020 (ES11) that describes the fields of completion records%
\footnote{https://262.ecma-international.org/11.0/\#table-8}, which we
model as follows:

@@

      \refine(\x : \ty, \true)(\aenv) &=&
      \aenv[ \x \mapsto \aty_\x \meet \{ \ty \} ]\\
      \refine(\x : \ty, \false)(\aenv) &=&
      \aenv[ \x \mapsto \aty_\x \setminus \{ \ty' \mid \ty' \subtype \ty
      \}]\\
      \refine(\expr, \bool)(\aenv) &=& \aenv\\
    \end{array}
  $}
  \vspace*{-0.5em}
\end{figure} \noindent
where $\aenv_j = \refine(\expr_j, \bool)(\aenv)$ for $j = 0, 1$,
$\aty_\expr = \aseme{\expr}(\aenv)$, and $\getSingle{\aty}$
returns $\{ \ty \}$ if $\aty$ denotes a singleton type $\ty$, or
returns $\emp$, otherwise.
